\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel} 
\usepackage{amssymb}
\usepackage{soul}
\usepackage{listings}
\usepackage{alltt}
\usepackage{underscore}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{ae}
\usepackage{amsmath}
\usepackage{amsfonts}
\PassOptionsToPackage{pdflatex}{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\graphicspath{ {data/} }

\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}


\usefonttheme{professionalfonts}


\title[Proyecto de Titulación]{Proyecto de Titulación}
\subtitle{Presentacion de avances (?)} 
\author[E. Regla]{Erik Regla} 
\institute[UTalca]{Universidad de Talca}
\date{\today} 

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

% introduccion y/o motivacion
% problema 
% metodlogia
% solución
% donde estoy


\begin{frame}
	Motivation
	\begin{itemize}
		\item None.
	\end{itemize}
  \end{frame}


\begin{frame}
	Introduction/Motivation
	\begin{itemize}
		\item Hardware-accelerated similarity search indices on the Adapteva Parallella-16 reconfigurable computing machine
	\end{itemize}
  \end{frame}


  \begin{frame}
	Problem
	\begin{itemize}
		\item Currently we already hit the atomical scale on transitor techonlogy.
		\item Focuses on research are pointing towards heterogenous architectures rather than homogeneous ones.
		\item There is work on using FPGAs as reconfigurable computing solutions, but there are no work related on metric space indexing.
	\end{itemize}
  \end{frame}



\begin{frame}
	Methodology
	\begin{itemize}
		\item We're gonna develop several prototypes for accelerators to test on our FPGA target.
		\item We're gonna compare the results agains a plain C (and memory coalesent/safe) implementation of an permutant index.
		\item Profit.
	\end{itemize}
  \end{frame}


\begin{frame}
	Solution
	\begin{itemize}
		\item Leverage a study on which techniques can be applied to an hybrid FS-PL solution in order to accelerate the proceses involved on a metric space indexing and searching.
		\item Implement such changes to our index
		\item Repeat.
	\end{itemize}
  \end{frame}


\begin{frame}
	Current status
	\begin{itemize}
		\item Rescheduling everything because of a WHOLE SEMESTER HIATUS.
		\item We're gonna implement a new upgrade for the algorithm, a segment-sorting variation for a network-sort.
		\item Check it out here https://github.com/KukyNekoi/fpga_index_accelerator
	\end{itemize}
  \end{frame}

\end{document}
